Draft Exploration

### 2020-04-02 draft_exploration.Rmd
playing around

hs_unsigned_list_ids <- master %>%
  filter(source == "H" & signed == "N") %>%
  select(player_id)

hs_unsigned_full <- hs_unsigned_list_ids %>%
  left_join(master, by = "player_id") %>%
  arrange(player_id, desc(year))
```

```{r}
hs_unsigned_full %>%
  filter(first_name == "Grayson" & last_name == "Byrd")
```

>>>>

list_unsigned_id <- master %>%
  filter(source == "H" & signed == "N") %>%
  select(player_id)

hs_unsigned <- hs_unsigned_list_ids %>%
  left_join(master, by = "player_id") %>%
  arrange(player_id, desc(year))
```

# filtered the data of unsigned high school picks with their subsequent drafts
# for only the first instance of the player being drafted, which is the draft
# afte their senior year of high school. For count_redrafted_hs, I filtered for
# draft_numb equal to 2 to see how many players were redrafted after originally
# turning the draft down.

count_unsigned_hs <- hs_unsigned_full %>%
  filter(draft_numb == 1) %>%
  count() %>%
  pull(n)

count_redrafted_hs <- hs_unsigned_full %>%
  filter(draft_numb == 2) %>%
  count() %>%
  pull(n)

percent_redrafted_hs <- round(count_redrafted_hs / (count_unsigned_hs), 2)

# below, I repeat the same process for high school players drafted in the top 10 and 20 rounds
